SciPy - some descriptive title here

### 2018-05-30 scipy-1.0/paper.tex
Drafted a short governance section.

>>>>

SciPy adopted an official Governance Document on August 3, 2017 (see PR\#6953). In summary,
we have a Benevolant Dictator for Life (BDFL) in Pauli Virtanen, and a (currently) 18
member Steering Council chaired by Ralf Gommers that i.e., decides on who gets commit rights.

SciPy adopted an official Code of Conduct on October 24, 2017 (see PR\#7963), drawing
inspiration from the Apache Foundation Code of Conduct, the Contributor Covenant,
the Jupyter Code of Conduct, and the Open Source Guides - Code of Conduct. In short,
we stated five specific guidelines: \emph{be open} (to anyone participating in our community),
\emph{be empathetic and patient} (in resolving conflicts), \emph{be collaborative} (we depend
on each other to build up the tools in the library), \emph{be inquisitive} (identifying issues
early on can be helpful to everyone), and \emph{be careful with wording} (no harassment or
exclusionary behavior). We outline a broad diversity inclusion statement, and provide
instructions for contacting the three members of our Code of Conduct Committee or an
external representative on the NumFOCUS Board of Directors.
